\documentclass{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{hyperref}


\begin{document}
\centerline{\LARGE{\bf{CSE206A Project: Fully Homomorphic Encryption}}}
\vspace{12.0pt}
\centerline{Michael Walter \hspace{0.1in} James Mouradian \hspace{0.1in} Victor Balcer}
\vspace{4.0pt}
\centerline{\today}
\vspace{14.0pt}

For our project we implemented fully homomorphic encryption, using the scheme
described in class and in lecture notes, using the Sage open-source mathematics
framework.

\section{Results}

We implemented a proof-of-concept NAND gate, since it is functionally complete.
The implementation is highly inefficient and features no algebraic
optimizations; our proof-of-concept takes approximately twenty minutes to
compute an encrypted NAND over two bits with the following parameters: $n=4$,
$q=64$, $Q=2^{25}$, and $\beta = 1$ (i.e. keys $s\in \mathbb{Z}_{64}^4$ and
$z\in\mathbb{Z}_{2^{25}}^4$). These are the smallest parameters for which we
can compute a NAND gate with error $\beta > 0$. To validate the gate, we
computed an encrypted NAND over two randomly generated bits and compared the
the decrypted output with the expected output. Decryption was successful across
twenty independent trials. The trials are meaningful; with increased error
the test reports both positive and negative results.

\section{Parameter Tuning}

Both key switching and homomorphic decryption work on parameters: $n=8$,
$q=128$, $Q=2^{17}$, and $\beta=1$. However, these parameters will fail to
compute a homomorphic NAND gate as the additional multiplication adds an error
factor of $n\log{Q}$. Based on the bounds from the formulas, we need to set
$Q \ge 2^{35}$. However, based on previous performance, we estimate the time
to perform this operation to take over 30 hours.

We did not rely on the formulas to compute our parameters. Because the formulas
ignore noise cancellation, they produce larger bounds, with significant time increases,
than are necessary for us to reliably calculate an encrypted NAND compared to those
found from our experimental tests.

\section{Limitations and Optimizations}

For very small parameters, the limiting factor of our code is matrix binary
decomposition. After trying several optimizations within Sage, we migrated
this to low-level compiled code called from within Sage; however, the type 
conversions to and from Sage matrices took longer than performing the 
decomposition in Sage itself. Ultimately, we used a compiled version of the 
decomposition code, with pre-allocated space for each matrix. Additionally,
we pre-computed all constant decomposition matrices of unit vectors used in
convolution for homomorphic decryption.

As parameters increase even slightly, matrix multiplication approaches the 
decomposition function with respect to running time. With realistic parameters
that add any remote degree of security to homomorphic operations, matrix 
multiplication will clearly dominate the running time of our implementation.

\section{Future Work}

There are three obvious improvements to be made on this implementation. The first is
to use CRT to represent elements in $\mathbb{Z}_q$ more efficiently. The second
is to use algebraic lattices, whose structure can be leveraged in order to
decrease the complexity of our implementation. The third is to focus on
implementation, using lower-level languages with hand-optimizations. Without
all of these in conjunction, the implementation will likely not ever become
fast enough to use for useful circuits in practice. 

\end{document}
